---
title: "Hotel bookings - data wrangling"
subtitle: "due Thursday, September 15 at 4:20pm"
output: 
  html_document:
    toc: true
    toc_float: true
    number_section: false
    highlight: tango
    theme: "cosmo"
link-citations: yes
editor: visual
editor_options: 
  markdown: 
    wrap: sentence
---

We will again work with data from the `nycflights13` package.

```{r, message = FALSE, warning = FALSE}
library(nycflights13)
library(tidyverse)
```


## Exercise 1

Examine the documentation for the datasets `airports`, `flights`, and `planes`. How are these datasets related? 

> YOUR ANSWER HERE

Suppose you wanted to make a map of the route of every flight. What variables would you need from which datasets? You need the geographic location of the airports (from `airports`) and the path of flights (i.e., which airports were involved) from `flights`.

We want to join flights to airports. Note these two datasets have no variables in common so we will have to specify the variable to join by using by =. Check out the documentation for more information.

```{r}
flights %>% 
  left_join(airports, by = c("dest" = "faa"))
```


## Exercise 2

Create a new dataset `dest_delays` with the median arrival delay for each destination. Note this question does not require you to use joins.

## Exercise 3

Create a new dataset by joining `dest_delays` and `airports`. Only include observations that have both delay and airport information. Note `dest_delays` and `flights` have no variables in common so you will need to specify the variables to join using by as in the example above.

## Exercise 4

Are all of the rows in `dest_delays` included in the new dataset you created by joining `dest_delays` and `airports`? Use an `anti_join` to help investigate this issue. Recall `anti_join(x,y)` returns all rows from `x` without a match in `y`.

```{r}

```

Google to see where the above airports are located.

## Exercise 5

Is there a relationship between the age of a plane and its delays? The plane tail number is given in the `tailnum` variable in the `flights` dataset. The year the plane was manufactured is given in the `year` variable in the `planes` dataset.

Start by finding the average arrival delay for each plane and store the resulting dataset in `plane_delays`.

```{r}

```

Join `plane_delays` to the planes data using an appropriate join and then use `mutate` to create an `age` variable. Note this data is from 2013.

```{r}

```

Finally, create an effective visualization of the data to investigate if there a relationship between the age of a plane and its delays. 

```{r}

```

